---
title: "A UN Report on Relationship between GDP and CO2"
author: "Jwilldigg"
date: "2023-01-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=FALSE}
library(tidyverse)
library(knitr)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read data, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

```{r gdp_lifeExp_1997-plot, echo=FALSE, fig.width=4, fig.width=3, fig.align='center'}
#make plot of GDP vs lifeExp
gapminder_1997 %>% ggplot(aes( x = gdpPercap, y = lifeExp, size = pop/1000000, color = continent)) + labs( x= "life Expectancy", y = "GDP per Capita", title = "Is There a Relationship Between GDP per Capita and Life Expectancy") +
  geom_point() + theme_classic()
```

```{r basic country-stats}
nCountries <- 
  gapminder_1997 %>%
  select(country) %>%
  n_distinct()

min_gdp <- gapminder_1997 %>% summarize(round(min(gdpPercap))) %>% pull() 

max_GDP <- gapminder_1997 %>% summarize(round(max(gdpPercap))) %>% pull()
```
The number of countries in the dataset is `r nCountries`.

# minimum gdp

The min gdp in the dataset is `r min_gdp`.

|HEADER 1|HEADER 2|
|-------------|-------------|
|row 1, column1|row 1, column 2|
|row 2, column1|row 2, column 2|

```{r table}
gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  kable()

```

